\chapter{Final Report Checklist}
\label{chapter:FinalReportCheckList}

\section{Requirements}
This document contains a checklist with items that are expected to be included in your EE1L1 IP-1
Final report. Experience shows that these items are covered in the Final reports with a large degree
of variability. Please note that these items are not new requirements; they are just a selection of already explicitly formulated requirements in the manual, particularly in the reporting templates (the rubrics included). The reason for signing these items out here is to support you in preparing a complete and well-argued report as much as possible.

The checklist contains items that should have already been present in the intermediate reports. There
are but three new items, first concerning the general Final report introduction, second about the very brief discussion on the selection between two designs (related to the power amplifier and filter sub-teams), third (optional) concerning the description of the booming bass solution.

A \textcolor{red}{penalty}/\textcolor{Green}{bonus} system is built into the checklist. The \textcolor{red}{penalty}/\textcolor{Green}{bonus} points must be regarded as maximums, with a full \textcolor{red}{penalty} applied when the relevant item is missing completely and the full \textcolor{Green}{bonus} awarded when the relevant item is dealt with and at an adequate level. Fractions of the \textcolor{red}{penalty}/\textcolor{Green}{bonus} points may be assigned as applicable.

\subsection{Introduction}
The complete functional audio system is presented and commented on. \textcolor{red}{Penalty -0.5 points}

\subsection{Power Supply Analysis}
Measurements, including waveform snapshots; comparison of the measured results with simulated and/or
analytic results, including an attempt to explain possible discrepancies. \textcolor{red}{Penalty -0.25 points}

\subsection{Loudspeaker Analysis}
The equivalent circuit for simulating Model 1 in Figure 4.2 and Model 2 in Figure 4.4 in Tutorial 2 is developed and discussed; simulated results are also provided. \textcolor{red}{Penalty -0.25 points}

\subsection{Passive Filter Design}
The design steps 1÷10 in Tutorial 3; penalty -0.25 points
(Not more than half a page) discuss the selection between the two designs of the two subteams and explain why your group decided to choose this design (and not the other design). \textcolor{red}{Penalty -0.25 points}

The partial simulated results (for the bass, mid, and tweeter parts) are added up, and the flat total result is illustrated (assuming an identical electric → acoustic transfer); deviations from the linear behavior are discussed and, possibly, commented. \textcolor{red}{Penalty -0.25 points}

Comparison between measured, simulated, and/or analytic results, including an attempt to explain possible discrepancies. \textcolor{Green}{Bonus 0.25 points}

\subsection{Power Amplifier Design}
(Not more than half a page) discuss the selection between the two designs of the two subteams and explain why your group decided to choose this design (and not the other design). \textcolor{red}{Penalty -0.25 points}

Simulation results. \textcolor{red}{Penalty -0.25 points}

Comparison between measured, simulated, and/or analytic results, including an attempt to explain possible discrepancies. \textcolor{red}{Penalty -0.25 points}