\chapter{Introduction}
\label{chapter:introduction}
\section{Introduction}

The \emph{'Booming Bass'} project challenges Electrical Engineering students to design and build an effective sound amplifier system collaboratively. The goal is to amplify a sound signal accurately, ensuring the speaker reproduces the input signal with minimal distortion. In this context, accuracy is defined by maintaining a flat frequency and acoustic response across the system. The project is divided into three primary sub-components: the power supply, the power amplifier, and the filters. 

Each sub-component undergoes a comprehensive design, simulation, and analysis process throughout the project. Initially, circuit analysis and calculations guide the development of theoretical models for each component. These models are then used in simulations to evaluate and assess an initial understanding of their performance. Finally, the components are then physically constructed and tested in the Tellegen Hall, allowing for further analysis of measurements and fine-tuning of the entire system. This iterative approach ensures that the final amplifier achieves the project's aim of accurate sound signal amplification.

This report presents the findings from each sub-component's design, simulation, and construction. It is structured to provide a clear progression of the work, beginning with methodologies, followed by design principles, simulation results, and measurements. This structure highlights the group's achievements and demonstrates the systematic approach to the development of the \emph{'Booming Bass'} sound amplifier system.



